Decision conformity: Battleship

### 2023-01-20 analysis/decisionConformityBattleship.Rmd
correlation between entropy effect and pclick cost

E2.click_log_with_boards_and_prior <-E2.click_log_with_boards %>%
  rowwise()%>%
  mutate(prior = get_group_prior(grid_number, click_number, board_state),
         prior_click = get_p_click(prior,flat_position),
         prior_entropy = get_prior_entropy(prior),
         prior_click_rank = get_prior_click_rank(prior,flat_position));

E2.click_log_with_prior_optimal <- E2.click_log_with_boards_optimal %>%
  mutate(prior = get_group_prior(grid_number, click_number, board_state),
         prior_click = get_p_click(prior,flat_position),
         prior_entropy = get_prior_entropy(prior),
         prior_click_rank = get_prior_click_rank(prior,flat_position),
         test_part=='optimal');

E2.click_log_with_prior_random <- E2.click_log_with_boards_random %>%
  mutate(prior = get_group_prior(grid_number, click_number, board_state),
         prior_click = get_p_click(prior,flat_position),
         prior_entropy = get_prior_entropy(prior),
         prior_click_rank = get_prior_click_rank(prior,flat_position),
         test_part = 'random')

@@

ggsave('../figures/E2_pclick_rank_misses_only.pdf',p)
ggsave('../figures/E2_pclick_rank_misses_only.png',p,width=5,height=2,dpi=300)

@@

>>>>

E2.click_log_with_boards_and_prior <-E2.click_log_with_boards %>%
  rowwise()%>%
  mutate(prior = get_group_prior(grid_number, click_number, board_state),
         prior_click = get_prior_click(prior,flat_position),
         prior_entropy = get_prior_entropy(prior),
         prior_click_rank = get_prior_click_rank(prior,flat_position));

E2.click_log_with_prior_optimal <- E2.click_log_with_boards_optimal %>%
  mutate(prior = get_group_prior(grid_number, click_number, board_state),
         prior_click = get_prior_click(prior,flat_position),
         prior_entropy = get_prior_entropy(prior),
         prior_click_rank = get_prior_click_rank(prior,flat_position),
         test_part=='optimal');

E2.click_log_with_prior_random <- E2.click_log_with_boards_random %>%
  mutate(prior = get_group_prior(grid_number, click_number, board_state),
         prior_click = get_prior_click(prior,flat_position),
         prior_entropy = get_prior_entropy(prior),
         prior_click_rank = get_prior_click_rank(prior,flat_position),
         test_part = 'random')

@@

ggsave('../docs/figures/E2_pclick_rank_misses_only.pdf',p)
ggsave('../docs/figures/E2_pclick_rank_misses_only.png',p,width=5,height=2,dpi=300)

@@

```{r entropy-pclick-correlation, echo=FALSE, cache=TRUE}

E2.entropy_summary <- E2.click_entropy_by_serial_position %>%
  filter(click_number>8) %>%
  group_by(subj_id,test_part) %>%
  summarise(entropy=mean(entropy,na.rm=T))

E2.p_click_summary <- E2.click_log_with_boards %>%
  rbind(E2.click_log_with_boards_random) %>%
  ungroup() %>%
  filter(click_number<8) %>%
  group_by(subj_id,test_part) %>%
  summarise(p_click=mean(p_click))

E2.p_click_summary %>%
  merge(E2.entropy_summary) %>%
  ggplot(aes(x=entropy,y=p_click, color=test_part))+
  geom_point(size=2,alpha=0.8)
